Your Paper Title

### 2025-05-13 Master Thesis/thesis.tex
New

\documentclass[12pt]{article}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{lmodern}  % 可选：提高 PDF 输出质量
\usepackage{indentfirst}
\usepackage{cancel}
\numberwithin{equation}{section}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\newcommand{\sket}[1]{|#1]}
\newcommand{\cbrak}[2]{\avg{#1}\![#2]}
\newcommand{\acbrak}[2]{[#1]\!\avg{#2}}
\onehalfspacing

@@

    {\LARGE \textbf{Tree Level Scattering Amplitudes in (De)Constructed Gauge Theory}}\\[1.5cm]

@@

Given a null momentum $p_\mu$ in four dimension spacetime, we can define a $2\times2$ matrix by sigma matrix 
\begin{equation*}
    p_{\alpha\dot{\alpha}}=p_\mu\sigma^\mu=\begin{pmatrix}
        p^0-p^3 & -p^1+ip^2\\
        -p^1-ip^2 & p^0+p^3
    \end{pmatrix}
\end{equation*}
note that det$p_{\alpha\dot{\alpha}}=0$ for massless particles, so it is always possible find two Weyl spinor(two components quantity) satsfying the following equation
\begin{equation}
    p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \label{2.1}
\end{equation}
For general complex momenta, the $\lambda_\alpha$ and $\tilde{\lambda}_{\dot{\alpha}}$ are independent two dimensional complex vectors. For real momenta, the matrix is Hermitian and 
so we have $\tilde{\lambda}_{\dot{\alpha}}=(\pm)(\lambda_\alpha)^*$.

@@

It is very easy to derive the following important relation:
\begin{equation}
    \cbrak{pq}{pq}=2p\cdot q= (p+q)^2
\end{equation}
by using \eqref{2.1} and 
\begin{equation*}
    \mathrm{Tr}(\sigma^\mu \bar{\sigma}^\nu)=2\eta^{\mu\nu}.
\end{equation*}

In amplitude calculations, \textbf{momentum conservation} is imposed on n particles as $\sum_{i=1}^{n}p_i^\mu=0$(here we consider all particles ingoing). Translating by 
spinor-helicity variable, it becomes
\begin{equation}
   \sum_{i=1}^{n}\aket{i}[i|=0,\quad \text{i.e.}\quad \sum_{i=1}^{n}\cbrak{qi}{ik}=0,
\end{equation}
here q and k are arbitrary light-like vectors.

@@

For example, the 4 gluon s-channel gives us
\begin{equation}
    \tilde{f}^{a_1a_2b}\tilde{f}^{ba_3a_4}=\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}{a_4})-\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_3}{a_4})-\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_4}{a_3})+\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_4}{a_3}).
\end{equation}
Similarly, three other diagrams can also be written in terms of single trace. Therefore, the full 4-point amplitude can be rewritten like
\begin{equation}
    \mathcal{A}_{4,\text{tree}}=g^2(A_4[1234]\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}{a_4})+\text{perms of } (234) )
\end{equation}
here the subamplitudes $A_4[1234],A_4[1243]$, etc. are called \textbf{color-ordereed ampltitudes}. This concept can be easily generalized to tree-level n-point case
\begin{equation}
    \mathcal{A}_{n,\text{tree}}=g^{n-2}\sum_{\sigma}A_n[1,\sigma(2,3\cdots n)]\mathrm{Tr}(T^{a_1}T^{\sigma(a_2\cdots}T^{a_n)})
\end{equation}
where the sun is taken over the $(n-1)!$ trace basis (considering the cyclic property of trace). Actually, the number of independent basis can be reduced to $(n-3)!$, called Del Duca-Dixon-Maltoni (DDM) color decomposition\cite{DelDuca:1999rs}. But it has no tight relation with this paper, so here we do not offer more detailed explanation for it.

@@

The color-ordered amplitudes have a number of properties
\begin{enumerate}
    \item \textit{Cyclic}: It follows from the cyclic property for trace that $A_n[12\cdots n]=A_n[2n\cdots 1]$
    \item \textit{Reflection}: $A_n[12\cdots n]=(-1)^nA_[n\cdots 21]$
    \item The $U(1)$ \textit{decoupling identity}: 
    \begin{equation}
        A_n[123\cdots n]+A_n[213\cdots n]+A_n[231\cdots n]+\cdots + A_n[23\cdots 1n]=0
    \end{equation}
\end{enumerate}
\subsection{BCFW recursion relation}

>>>>

\documentclass[12pt]{article}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{lmodern}  % 可选：提高 PDF 输出质量
\usepackage{indentfirst}
\usepackage{cancel}
\usepackage{xcolor}
\numberwithin{equation}{section}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\newcommand{\sket}[1]{|#1]}
\newcommand{\cbrak}[2]{\avg{#1}\![#2]}
\newcommand{\acbrak}[2]{[#1]\!\avg{#2}}
\newcommand{\tif}[1]{\textit{\textbf{#1}}}
\onehalfspacing

@@

    {\LARGE \textbf{On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory}}\\[1.5cm]

@@

Given a null momentum $p_\mu$ in four dimension spacetime, we can define a $2\times2$ matrix by sigma matrix 
\begin{equation*}
    p_{\alpha\dot{\alpha}}=p_\mu\sigma^\mu=\begin{pmatrix}
        p^0-p^3 & -p^1+ip^2\\
        -p^1-ip^2 & p^0+p^3
    \end{pmatrix}
\end{equation*}
note that det$p_{\alpha\dot{\alpha}}=0$ for massless particles, so it is always possible find two Weyl spinor(two components quantity) satsfying the following equation
\begin{equation}
    p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \label{2.1}
\end{equation}
and similarly we can obtain define
\begin{equation}
    p_\mu \bar{\sigma}^\mu=p^{\dot{\alpha}\alpha}=\tilde{\lambda}^{\dot{\alpha}}\lambda^\alpha=\sket{\lambda} \langle \lambda |,
\end{equation}
For general complex momenta, the $\lambda_\alpha$ and $\tilde{\lambda}_{\dot{\alpha}}$ are independent two dimensional complex vectors. For real momenta, the matrix is Hermitian and 
so we have $\tilde{\lambda}_{\dot{\alpha}}=(\pm)(\lambda_\alpha)^*$.

@@

It is very easy to derive the following important relation:
\begin{equation}
    \cbrak{pq}{pq}=2p\cdot q= (p+q)^2
    \label{2.7}
\end{equation}
by using \eqref{2.1} and 
\begin{equation*}
    \mathrm{Tr}(\sigma^\mu \bar{\sigma}^\nu)=2\eta^{\mu\nu}.
\end{equation*}
Here, we list other identities without any provement
\begin{align}
    &[k|\gamma^\mu\aket{p}=\langle p|\gamma^\mu |k],\\
    &{[k|\gamma^\mu\aket{p}}^*=[p|\gamma^\mu\aket{k} \qquad \text{(for real moemnta)}.
\end{align}
and \textbf{Fierz identity}
\begin{equation}
    \langle 1|\gamma^\mu |2]\langle 3|\gamma_\mu |4]=2\cbrak{13}{24}
\end{equation}
will be used in several times.
In amplitude calculations, \textbf{momentum conservation} is imposed on n particles as $\sum_{i=1}^{n}p_i^\mu=0$(here we consider all particles ingoing). Translating by 
spinor-helicity variable, it becomes
\begin{equation}
   \sum_{i=1}^{n}\aket{i}[i|=0,\quad \text{i.e.}\quad \sum_{i=1}^{n}\cbrak{qi}{ik}=0,
\end{equation}
here q and k are arbitrary light-like vectors.

@@

For example, the 4 gluon s-channel gives us
\begin{equation}
    \tilde{f}^{a_1a_2b}\tilde{f}^{ba_3a_4}=\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}T^{a_4})-\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_3}T^{a_4})-\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_4}T^{a_3})+\mathrm{Tr}(T^{a_2}T^{a_1}T^{a_4}T^{a_3}).
\end{equation}
Similarly, three other diagrams can also be written in terms of single trace. Therefore, the full 4-point amplitude can be rewritten like
\begin{equation}
    \mathcal{A}_{4,\text{tree}}=g^2(A_4[1234]\mathrm{Tr}(T^{a_1}T^{a_2}T^{a_3}T^{a_4})+\text{perms of } (234) )
\end{equation}
here the subamplitudes $A_4[1234],A_4[1243]$, etc. are called \textbf{color-ordereed ampltitudes}. This concept can be easily generalized to tree-level n-point case
\begin{equation}
    \mathcal{A}_{n,\text{tree}}=g^{n-2}\sum_{\sigma}A_n[1,\sigma(2,3\cdots n)]\mathrm{Tr}(T^{a_1}T^{\sigma(a_2\cdots}T^{a_n)})
    \label{2.29}
\end{equation}
where the sun is taken over the $(n-1)!$ trace basis (considering the cyclic property of trace). Actually, the number of independent basis can be reduced to $(n-3)!$, called Del Duca-Dixon-Maltoni (DDM) color decomposition\cite{DelDuca:1999rs}. But it has no tight relation with this paper, so here we do not offer more detailed explanation for it.

@@

The color-ordered amplitudes have a number of properties
\begin{enumerate}
    \item \textit{Cyclic}: It follows from the cyclic property for trace that $A_n[12\cdots n]=A_n[2n\cdots 1]$
    \item \textit{Reflection}: $A_n[12\cdots n]=(-1)^nA_[n\cdots 21]$
    \item The $U(1)$ \textit{decoupling identity}: 
    \begin{equation}
        A_n[123\cdots n]+A_n[213\cdots n]+A_n[231\cdots n]+\cdots + A_n[23\cdots 1n]=0
    \end{equation}
\end{enumerate}

The trace basis \eqref{2.29} is overcomplete implies that there are further linear relations among these subamplitudes, which are called 
\textit{\textbf{Kleiss - Kuiff(KK) relations}} 
\begin{equation}
    A_n[1,\{\alpha\},n,\{\beta\}]=(-1)^{|\beta|}\sum_{\sigma\in \text{OP}(\{\alpha\},\{\beta^T\}) }A_n[1,\sigma,n]
\end{equation}
where $\beta^T$ denotes the reverse ordering of the labels $\{\beta\}$  and the sum is over ordered
permutations “OP”, means permutations of the labels in the joined set $\{\alpha\}\cup \{\beta^T\}$ in which 
the ordering within $\{\alpha\}$ and $\{\beta\}^T$ is preserved.

Consider a 5-point case as an example. Taking the LHS to be $A_5[1,\{2\},5,\{3,4\}]$, we have $\{\alpha\}\cup \{\beta^T\}=\{2\}\cup \{4,3\}$, so the 
ordered permutations $\sigma$ refers to $\{243\},\{423\},\{432\}$. Thus the KK relation reads
\begin{equation}
    A_5[12534]=A_5[12435]+A_5[14235]+A_5[114325].
\end{equation}

The KK relations combine with cyclic, reflection, and $U(1)$ decoupling identities reduce the number of independent
basis to $(n-2)!$. However, there are further linear relations called $\textit{\textbf{BCJ relations}}$ -- named after Bern, Carrasco and Johansson, which further
reduce the number to $(n-3)!$.

Although I will not show the derivation of BCJ relations, I would like to give some examples
\begin{gather}
    s_{14}A_4[1234]-s_{13}A_4[1243]=0,\\
    s_{12}A_5[21345]s_{23}A_5[13245]-(s_{23}+s_{24})A_5[13425]=0.
\end{gather}
\subsection{Little group scalling}
The rich structure of scattering amplitudes can be originated from a fundamental question — “What is a particle?” — which relates directly to Wigner’s Little group notation,
characterizing how particles transform under Lorentz symmetry. Following this thought, we think particle as a unitary representation of 
Poincar$\acute{e}$ group, which is the symmetry group of our spacetime. We use two labels to denote a one-particle state, one is the momentum $p^\mu$, another is $\sigma$ representing
other labels the particle ca carry.

We start from a one-particle state $\aket{k;\sigma}$ with reference momentum $k$. Another momentum $p$ is related by the lorentz transformation $L(p;k)$, $p=L(p;k)k$. Obviously, this Lorentz transformation is
not unique because there exist Lorentz transformations keeping p invariant, called ``Little group transformation''.  We assume that there exist a 
unitary representation for the Lorentz group, the operator in Hillbert space are denoted like $U(\Lambda)$.

Then we simply \textit{define} the one-particle state with momentum p as 
\begin{equation}
    \aket{p;\sigma}=U(L(p;k))\aket{k;\sigma}.
\end{equation}
Having made this definition, we can compute how the state transformed under a general Lorentz transformation
\begin{equation}
    U(\Lambda)|p,\sigma\rangle = U(\Lambda) U(L(p;k))|k,\sigma \rangle = U(L(\Lambda p;k)) U(L^{-1}(\Lambda p;k) \Lambda L(p;k)) |k,\sigma \rangle\,.
\end{equation}
here we use the fact $U(\Lambda_1\Lambda_2)=U(\Lambda_1)U(\Lambda_2)$.
Notice that $W(\Lambda,p,k)$ is not a general transformation but keep the momentum k invariant $Wk=k$. This subgroup of Lorentz group is called little group.
Thus we must have 
\begin{equation}
    U(W(\Lambda,p,k))\aket{k;\sigma}=D_{\sigma\sigma^{'}}(W(\Lambda,p,k))\aket{k,\sigma^{'}},
\end{equation} 
where $D_{\sigma\sigma^{'}}$ is the representation for little group. Then, p should transformed like
\begin{equation}
     U(\Lambda)|p,\sigma\rangle=D_{\sigma\sigma^{'}}(W(\Lambda,p,k))\aket{\Lambda p,\sigma^{'}}
\end{equation}

The scattering amplitudes for n particle should keep invariant under Poincar$\acute{e}$ transformation -- translation invariance and Lorentz invariance
\begin{gather}
    \mathcal{M}(p_a,\sigma_a)=\delta^D(p_1^\mu+\cdots +p_n^\mu)\mathcal{M}(p_a,\sigma_a)\\
    \mathcal{M}^\Lambda(p_a,\sigma_a)=\prod_{a}(D_{\sigma\sigma^{'}})\mathcal{M}((\Lambda p)_a,\sigma_a^{'})
    \label{2.43}
\end{gather}

In D spacetime dimensions, the little group for massive particles is $SO(D-1)$. For massless
particles the little group is the the group of Euclidean symmetries in (D−2) dimensions, which
is $SO(D-2)$.In this article, we mainly discuss massless particles scattering in 4 dimension spacetime, so the little group is $SO(2)\backsimeq U(1)$.

Then from the definition of spinor-helicity variable\eqref{2.1}, we can notice that there is an ambiguity here.
The momentum is invariant under the following redefinition
    \begin{equation}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C} 
    \end{equation}
    same for
    \begin{equation}
        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation}.
This scale perfectly matches the $U(1)$ little group transformation, so we can identify this rescale as the little group transformation.
The scattering amplitudes should transform \textcolor{red}{covariantly} under little group scaling like \eqref{2.43}, so
\begin{equation}
    \color{red} \mathcal{A}_n(\{\aket{1},\sket{1},h_1\},\ldots\{t_i^{-1}\aket{i},t_i\sket{i},h_i\},\ldots )=t_i^{2h_i}\mathcal{A}_n
    \label{2.46}
\end{equation}
where $h_i$ refers to the helicity of particles.
As an example, consider the QED amplitude, $A_3(f^-\bar{f}^+\gamma^-)=e\frac{\avg{13}^2}{\avg{12}}$. For the negative helicity photon (particle 3), we obtain $t_3^{-2}=t_3^{2(-1)}$.
We will see that little group scaling plays a significant role in 3-particle amplitudes.

\noindent
\textbf{3-particle amplitudes}

\noindent
By 3-particle special kinematics, we have known that on-shell 3-point amplitudes depends on either square brackets or
angle brackets. We suppose that it only depends on angle brackets. We can write down the general ansatz
\begin{equation}
     A_3(1^{h_1},2^{h_2},3^{h_3})=c\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}},
\end{equation}
where c is just a constant. Little group scaling \eqref{2.46} tell us that
\begin{equation}
    t_1^{2h_1} A_3(1^{h_1},2^{h_2},3^{h_3})=ct_1^{-x_{12}}t_1^{-x_{13}}\avg{12}^{x_{12}}\avg{13}^{x_{13}}\avg{23}^{x_{23}}.
\end{equation}
We can obtain
    \begin{equation}
        2h_1=-x_{12}-x_{13}
    \end{equation}
    Similarly, we can also obtain
    \begin{equation}
        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
    \end{equation}
    Then all index can be solved from this system of equations, so that
 \begin{align}
    A_3^{h_1h_2h_3} &= c\langle12\rangle^{h_3-h_1-h_2} \langle31\rangle^{h_2-h_1-h_3} \langle23\rangle^{h_1-h_2-h_3}
    && \quad h_1 + h_2 + h_3 < 0 \label{2.51}\\[0.5em] 
    A_3^{h_1h_2h_3} &= c' [12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}
    && \quad h_1 + h_2 + h_3 > 0 \label{2.52}
\end{align}
This means that \textit{\textbf{all massless 3-point amplitudes are completely fixed by little group scaling!}}

We have shown the 3-point QED amplitudes. So now we can consider something different -- 3-point gluon amplitudes with 2 same helicities and 1 different helicity.
Then we can determine the amplitudes from \eqref{2.51} \eqref{2.52}
\begin{equation}
    A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}, \quad A_3(g_1^+,g_2^+,g_3^-)=g\frac{[12]^3}{[23][31]} \label{2.53}
\end{equation}

Here it need some efforts to explain about the condition after equation \eqref{2.51} and \eqref{2.52}.If we assume the amplitude
$A_3(g_1^-,g_2^-,g_3^+)$ depending on square brackets, so can obtain a different expression
\begin{equation}
    A_3(g_1^-,g_2^-,g_3^+)=g^{'}\frac{[31][23]}{[12]^3},
    \label{2.54}
\end{equation}
to distinguish these two possibilities, we need to use \textbf{dimension analysis}. From \eqref{2.7}, we can know that both square brackets and angle brackets have mass-dimension 1. 
Thus the kinematic factor of amplitude \eqref{2.53} has mass-dimension 1, compatible with the interaction term $AA\partial A$ in $\mathrm{Tr}F_{\mu\nu}F^{\mu\nu}$. But the mass-dimension 
of kinematic factor in \eqref{2.54} is (-1), so it should come from the interaction term like $g^{'}AA\frac{1}{\square }A$. Here, we only consider the local field theory, so this kind of interaction
should be discarded.

The combination of \tif{little group scaling} and \tif{locality} uniquely fixes the massless 3-point amplitudes. In general, 
\begin{equation}
    \text{An n-point amplitude in D=4 spacetime have mass-dimension 4 - n.}
\end{equation}
Although we discard the amplitude \eqref{2.54}, the coupling s¥constant $g^{'}$ have mass-dimension 2, so \eqref{2.54} has the correct mass-dimension as \eqref{2.53}.

How about the gluon amplitude with all minus helicities? The formula \eqref{2.51} immediately tells that it should equal to
\begin{equation}
    A_3(g_1^-,g_2^-,g_3^-)=g^{''}\mdavg{12}{23}\!\avg{31}.
\end{equation}
The kinematic part has mass-dimension 3 and reveals that: 
\begin{enumerate}
    \item The coupling constant $g^{''}$ must have mass-dimension -2.
    \item This must come from an interaction term with 3 derivatives like $(\partial A)^3$.
\end{enumerate}
Furthermore, kinematic part has the antisymmetry under the exchange of gluon momenta, so the coupling constant should 
also have this antisymmetry in order to satisfy the Bose statics as is of course the pure Yang-Mills case. 
The natural candidate of this amplitude is a dimension 6 operator $\mathrm{Tr}F^\mu_\nu F^\nu_\lambda F^\lambda _\mu$.

\subsection{MHV Classification}
It has been well known that the all-plus tree-level gluon amplitudes vanish
\begin{equation}
    \text{tree-level gluon amplitues}: \quad A_n[1^+,2^+,\cdots,n^+]=0 \quad\text{and}\quad A_n[1^+,2^+,\cdots,n^-]=0
\end{equation}
This conclusion holds for the case with all helicities flipped:
\begin{equation}
    \text{tree-level gluon amplitues}: \quad A_n[1^-,2^-,\cdots,n^-]=0 \quad\text{and}\quad A_n[1^-,2^-,\cdots,n^+]=0
\end{equation}
In supersymmetric Yang-Mills theories, these results hold for all loop order, so actually it is a special case for SYM.

If we flip one more helicit, the situation becomes quite different. Amplitudes $A_n[1^-,2^-,3^+,\cdots,n^+]$ does not equal to 0 and is quite important called \textbf{MHV amplitudes}.
The gluon amplitudes with two negative helicities and n - 2 positive helicities are called
\tif{maximally helicity violating} – or simply \tif{MHV} for short. The concept ``maximally helicity violating'' comes from thinking a $2\rightarrow n-2$ scattering process. 
Because of crossing symmetry, the outgoing particle with positive(negtive) helicity is equivalent with an ingoing particle with negative(positive) helicty. So if we consider the process $A_n[1^+,2^+,\cdots,n^+]$ with 
all particle ingoing. It crosses over to $1^+2^-+\rightarrow 3^-\cdots n^-$ with two ingoing particles and n-2 outgoing particles, that's the reason we call it ``helicity violating''. We have known that the process in which the most we can violate helicity
is $1^+2^+\rightarrow 3^+4^+5^-\cdots n^-$, which is equivalent to amplitudes $A_n[1^+2^+3^-4^-5^+\cdots n^+]$, therefore it is the \textit{maximally helicity violating} process.

As we have shown in the last subsection, the MHV gluon tree amplitudes are given by Parke - Talyor formula
\begin{equation}
    A_n[1^+\cdots i^-\cdots j^- \cdots n^+]=\frac{\avg{ij}^4}{\mdavg{12}{23}\cdots\avg{n1}}
\end{equation}
The MHV amplitudes are the important blocks for scattering amplitudes in (super)Yang-Mills theory. They are simplest amplitudes, and the next-to simplest
are called \textbf{Next-to-MHV} amplitudes, or just \textbf{NMHV}. This refers to scattering process for which two 2 positive gluons scatter into 3 positive gluons and n-5 negative gluons. 
Similarly, we can define \textbf{$N^k$MHV} amplitudes. For anti-MHV amplitudes with all helicities flipping, we have a formula
\begin{equation}
    A_n[1^-\cdots i^+\cdots j^+ \cdots n^-]=\frac{[ij]^4}{[12][23]\cdots[n1]}.
\end{equation}
\subsection{BCFW recursion relation}
The BCFW recursion relation was introduced in 2005 by Britto, Cachazo, and Feng, and later extended with Witten. It provided a novel way to compute tree-level scattering amplitudes by 
analytically continuing external momenta into the complex plane and expressing higher-point amplitudes recursively in terms of lower-point ones. This on-shell approach uncovered surprising 
simplicity in gauge theory amplitudes and offered an alternative to the traditional Feynman diagram expansion. The method was inspired in part by Witten's twistor string theory and the MHV 
diagram program. In parallel, off-shell recursion relations were also being explored, especially in background field methods and Berends-Giele recursion, which organize amplitudes based on 
off-shell currents. While off-shell methods remain useful in certain computational frameworks, the BCFW recursion highlighted the power of staying strictly on-shell, leading to a deeper understanding 
of symmetry, analyticity, and the geometry of scattering processes. It has since become a cornerstone of modern amplitude research.

Beyond BCFW, other on-shell recursion relations have also emerged—for instance, the KLT relations linking gauge and gravity amplitudes, and the double copy structure as well as recursion 
for theories with special helicity configurations or massive particles. Together, these developments form the foundation of modern amplitude methods, emphasizing physical principles like unitarity, analyticity, 
and factorization over traditional Lagrangian-based techniques.

\subsubsection{Complex shift and Relation from Simple Cauchy's Theorem}
An on-shell amplitude(each external leg satisfies on-shell condition) is labeled by their external momentum $p_\mu$ and hilicity $h_i$.
Here we only consider the massless particles $p_i^2=0$, for $i=1,2,\cdots,n$. And momentum conservation $\sum_{i=1}^{n}p_i^\mu=0$ should hold.

First, let us consider the most general case. We need to introduce n complex-valued vectors $r_i^\mu$ subject to 
\begin{itemize}
    \item $\sum_{i=1}^{n}r_i^\mu=0$,
    \item $r_i\cdot r_j=0$ for all $i,j=1,2,\cdots ,n$. In particular, $r_i^2=0$,
    \item $p_i\cdot r_i=0$ for each i(no sum).
\end{itemize}
These vectors $r_i$ are used to define n shifted momentum
\begin{equation}
    \hat{p}_i^\mu\equiv p_i^\mu+zr_i^\mu\quad \text{with}\quad z\in \mathcal{C}
\end{equation}
Note that, by imposing these constraints,
\begin{itemize}
    \item Momentum conservation holds for the shifted momentum:
\end{itemize}
